\thetitle

### 2018-01-10 TeX/manuscript.tex
Added diagrams to 2.7

\textcolor{red} {Next Step? figure out how to convert from categorical to numerical.}

>>>>

\subsection{Using conditional expressions to vary computations of neurons}

Consider a simple network with two input neurons, two corresponding weights, and a single output neuron.

\begin{figure}

	\tikzstyle{input} = [shape=circle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = green!32]
	\tikzstyle{output} = [shape=circle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = blue!32]
	\tikzstyle{weight} = [thick,midway,sloped,above,->]

	\node[input] (i1) at (0,0) {8};
	\node[input] (i2) at (4,0) {5};

	\node[output] (o1) at (2,2) {14};

	\draw[->](i1) -> (o1) node[weight] {0.5};
	\draw[->](i2) -> (o1) node[weight] {2};

\caption{A simple feed-forward neural network with two inputs and one output.}

In the above network, the output neuron's value is calculated as a weighted sum of the inputs. While this algorithm is widely used in feed-forward neural networks, it assumes that the desired output value's relationship to it's inputs can be modelled by a weighted sum of the inputs.

Suppose we wanted to construct a network that returns the number of times older one person is than another. Given the inputs of 24 and 8, the output would be 3 since a 24-year-old is 3 times older than an 8-year-old. However, this relationship cannot be expressed through a weighted sum, since no weighted sum of two variables will always equal the quotient of the two variables. To deal with this problem, we will introduce a 'router' that will allow for more than just a weighted sum to define the output.

\begin{figure}

	\tikzstyle{input} = [shape=circle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = green!32]
	\tikzstyle{output} = [shape=circle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = blue!32]
	\tikzstyle{router} = [shape=rectangle, draw, outer sep=0,inner  sep=6,minimum size=15, fill = red!32]
	\tikzstyle{op} = [shape=rectangle, draw, outer sep=0,inner  sep=6,minimum size=18]
	\tikzstyle{weight} = [thick,midway,sloped,above,->]

	\node[input] (i1) at (0,0) {Age 1};
	\node[input] (i2) at (4,0) {Age 2};

	\node[router] (r) at (2,2) {Router};

	\node[op] (op1) at (0,4) {$\div$};
	\node[op] (op2) at (4,4) {$+$};

	\node[output] (o1) at (2,6) {14};

	\draw[->](i1) -> (r) node[weight] {};
	\draw[->](i2) -> (r) node[weight] {};

	\draw[->](r) -> (op1) node[weight] {};
	\draw[->](r) -> (op2) node[weight] {};

	\draw[->](op1) -> (o1) node[weight] {};
	\draw[->](op2) -> (o1) node[weight] {};
